Rule-Based Preordering on Multiple Syntactic Levels in Statistical Machine Translation

### 2014-09-24 Paper/paper.tex
.

\section{Multi-Level-Tree Reordering}
\subsection{Reordering on Multiple Syntactic Levels}

@@

\begin{figure}
\centering
\scalebox{1.3}{\input{unstructured.tikz}}
\caption{Detection of reordering pattern from multiple syntactic levels}
\label{unstructured}
\end{figure}

@@

\begin{figure}
\centering
\scalebox{1.3}{\input{extract.tikz}}
\caption{A phrase with its syntax tree and alignment for rule extraction}
\label{extract}
\end{figure}

>>>>

\section{Multi-Level-Tree Reordering}

Our preordering method is based on reordering rules. Reordering rules show how sentences should be reordered in source language before translation. In our system, the rules are generated by using the word alignment, and syntax tree, all of which are calculated based on the training data. After reordering rules are applied to the source sentences, word lattices are generated. A word lattice contains all the reordering possibilities of a source sentence and is further passed to the decoder for translation. The preordering system could be illustrated as figure~\ref{prereordering}.

\begin{figure*}
\centering
\input{prereordering.tikz}
\caption{Illustration of preordering system}
\label{prereordering}
\end{figure*}

\subsection{Reordering on Multiple Syntactic Levels}

@@

\begin{figure}
\centering
\input{unstructured.tikz}
\caption{Detection of reordering pattern from multiple syntactic levels}
\label{unstructured}
\end{figure}

@@

\begin{figure}
\centering
\input{extract.tikz}
\caption{A phrase with its syntax tree and alignment for rule extraction}
\label{extract}
\end{figure}
